Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Changes to Introduction

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. Since the observed
characteristics of these subjects are very similar, similarity of their
unobserved characteristics is often credible as well, and differences in the
outcomes between the treated and untreated can be plausibly attributed to the
treatment alone. As a practical matter this involves comparing units within a
bandwidth just above and just below the threshold.

@@

In these studies, identification occurs exactly at the cutoff, so the
treatment effect is typically estimated by fitting separate local linear models
above and below the cutoff, then extrapolating the models to the exact point of
discontinuity. The difference between the estimated effects at that point is
taken to be an estimate of the treatment effect. As a practical matter, the key
econometric issue is determining the bandwidth for the local linear models.  One
very popular choice is the bandwidth estimator proposed by \cite{IK} and
extended by \cite{calonico2014}, which minimizes the Asymptotic Mean Squared
Error of difference in the models' point estimators at the cutoff.

>>>>

\newpage
\section{Introduction}
Regression Discontinuity (RD) designs have emerged in the last decade as an
important and popular research design strategy for analyzing the causal impact
of policies and interventions in several fields of the social sciences,
including economics, political science, public policy, and sociology.
This research strategy exploits the fact that many programs use somewhat
arbitrary thresholds to determine whether or not to provide a ``treatment,''
usually relying on some type of score, which this literature calls a ``running
variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
certain threshold receive treatment while the ones below that cutoff are left
untreated.
The identification of the treatment effect at the threshold is then based on
comparing treated and untreated units at the cutoff. Since being just above
or below the arbitrary cutoff is credibly not related to other factors impacting
outcomes, including their unobserved characteristics,  differences between 
treated and untreated individuals at the cutoff can be plausibly attributed to the
treatment alone. As a practical matter this involves comparing units within a
bandwidth just above and just below the threshold.

@@

In these studies, identification occurs exactly at the cutoff, so the
treatment effect is typically estimated by fitting separate local linear models
above and below the cutoff, then extrapolating the models to the exact point of
discontinuity. The difference between the estimated outcomes at that point is
taken to be an estimate of the treatment effect. As a practical matter, a key
econometric issue is determining the bandwidth for the local linear models.  One
very popular choice is the bandwidth estimator proposed by \cite{IK} and
extended by \cite{calonico2014}, which minimizes the Asymptotic Mean Squared
Error (AMSE) of difference in the models' point estimators at the cutoff.
